Radio Emission from Red-Giant Hot Jupiters

### 2015-09-14 ms.tex
minor edits

\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?
\memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' 
or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}}

@@

One of the key features that makes planetary radio emission distinct is the almost complete circular polarization \citep[e.g.][]{dulk1994}.
...\memoYF{write here (YF)}

Another key is the significant time variability of the planetary radio emission. 
The potential factors that cause time variability are  listed below.

\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis. If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation. 
%
\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because the presence of Io inputs plasmas into the system. 
Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.

\paragraph{Variability of stellar wind (a few months $\sim $)?}
If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time-variabililty of planetary radio emission.  Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.

@@

\memoYF{Need to elaborate. References are needed. }

So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
Therefore, one possible strategy is to target known planetary systems.  
One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox{m/s}$. 
Therefore, there are some parameter spaces where current radial velocity observations cannot survey. For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.

@@

Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes. In turn, we could utilize the time variability to characterize the system. For example, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets. 
If the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).

@@

In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind. 
Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
Based on such a picture, the massive stellar wind of a red giant or AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
We found that the intrinsic brightness of radio emission from RGHJs would be comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 15 MHz$ for typical red giants and $\sim 464 MHz$ for typical AGB stars. 
The most promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).

@@

Once the planetary radio emission is detected, ...\memoYF{write here}.

>>>>

\title{Radio Emission from Red-Giant Hot Jupiters}

@@

One of the key features that makes planetary radio emission distinct is the nearly  complete circular polarization \citep[e.g.][and reference therein]{dessler1983}. 
On the other hand, active galactic nuclei, which are the major confusion sources, are known to have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014}.

Another key is the significant time variability of the planetary radio emission. 
The factors that influence time variability are listed below.

\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis. If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation. 
%
\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because Io disturbs the surrounding electromagnetic field. 
Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.

\paragraph{Variability of stellar wind (a few months $\sim $)?}
If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variabililty of planetary radio emission.  Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.

@@

So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
Therefore, one possible strategy is to target known planetary systems.  
One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30$ [m/s]. 
Therefore, there are some parameter spaces where current radial velocity observations have not been able to survey. For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.

@@

Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes. In turn, we could utilize the time variability to characterize the system. For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable. 
Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply presence of satellites.

@@

In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind. 
Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
Based on such a picture, the massive stellar wind of a red giant or AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars.

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars. 
The promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).

@@

The radio intensity of the RGHJs are intrinsically $>100$ times brighter than the main-sequence counterparts. This indicates that they can be observed 10 times further away, or in 1000 times larger volume. 
This can compensate the rareness of the evolved stars at least partly. Thus, RGHJs will be reasonable targets for future search for radio lighthouse from planetary systems.

Radio emission can be follow-up observations of known RGHJs or may also be used as probe to discover them, given the lowered sensitivity of  radial velocity methods in detecting planetary companions. 
Once the planetary radio emission is detected, it will provide a unique approach to  planetary spin, magnetic field, and presence of satellite, and potentially stellar wind properties.
